Cross-Validation Default

### 2023-07-03 minos/validation/cross_validation_default.Rmd
Dropped dead people from output dataframes and removed missing values from mean plots. Cleaned up some sections of the cross_validation_default script also

```{r, include=FALSE}
# cross validation simulation output
#out.path <- 'Minos/output/cross_validation/'
out.path <- here::here('output', 'cv')
cv1 <- read_singular_local_out(here::here(out.path, 'default1/'), 'baseline')
cv2 <- read_singular_local_out(here::here(out.path, 'default2/'), 'baseline')
cv3 <- read_singular_local_out(here::here(out.path, 'default3/'), 'baseline')
cv4 <- read_singular_local_out(here::here(out.path, 'default4/'), 'baseline')
cv5 <- read_singular_local_out(here::here(out.path, 'default5/'), 'baseline')

@@

```{r}
multi_year_boxplots(raw, cv, 'nutrition_quality')
```

@@

```{r}
tobacco.pivoted <- combine_and_pivot_long(df1 = cv, 
                                       df1.name = 'simulated', 
                                       df2 = raw, 
                                       df2.name = 'raw', 
                                       var = 'ncigs')

plot_mean_comparison(pivoted.df = tobacco.pivoted, 
                     var = 'ncigs', 
                     group.var = 'scenario',
                     save = FALSE)

>>>>

```{r, include=FALSE}
# cross validation simulation output
#out.path <- 'Minos/output/cross_validation/'
out.path <- here::here('output', 'cv')
cv1 <- read_singular_local_out(here::here(out.path, 'default1/'), 'baseline', drop.dead = TRUE)
cv2 <- read_singular_local_out(here::here(out.path, 'default2/'), 'baseline', drop.dead = TRUE)
cv3 <- read_singular_local_out(here::here(out.path, 'default3/'), 'baseline', drop.dead = TRUE)
cv4 <- read_singular_local_out(here::here(out.path, 'default4/'), 'baseline', drop.dead = TRUE)
cv5 <- read_singular_local_out(here::here(out.path, 'default5/'), 'baseline', drop.dead = TRUE)

@@

```{r}
cv.mean.plots(cv1, cv2, cv3, cv4, cv5, raw, 'nutrition_quality')
multi_year_boxplots(raw, cv, 'nutrition_quality')
```

@@

```{r}
cv.mean.plots(cv1, cv2, cv3, cv4, cv5, raw, 'ncigs')
